Analytic Doppler Imaging

### 2019-08-08 tex/gitlinks.tex
working on the paper figs

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-08 tex/ms.tex
working on vogtstar
added vogtstar fig
misc
working on the paper figs

\newcommand{\sT}{\bvec{s}^\top}
\newcommand{\R}{\bvec{R}}
\newcommand{\AOne}{\bvec{A_1}}
\newcommand{\alm}{\bvec{a}}
\newcommand{\x}{\bvec{x}}
\newcommand{\kT}{\bvec{k}^\top}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Doppler}{\bvec{D}}
\newcommand{\Surf}{\mathcal{S}}
\newcommand{\Curve}{\mathcal{C}}
\newcommand{\Dargs}{\bvec{d}}
\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}

@@

@@

Specifically, the $n^\mathrm{th}$ term of the polynomial basis

>>>>

\newcommand{\sT}{\bvec{s}^\top}
\newcommand{\R}{\bvec{R}}
\newcommand{\AOne}{\bvec{A_1}}
\newcommand{\alm}{\bvec{a}}
\newcommand{\x}{\bvec{x}}
\newcommand{\kT}{\bvec{k}^\top}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Doppler}{\bvec{D}}
\newcommand{\Surf}{\mathcal{S}}
\newcommand{\Curve}{\mathcal{C}}
\newcommand{\Dargs}{\bvec{d}}
\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
\newcommand{\vogtstar}{\texttt{VOGTSTAR}\xspace}

@@

\section{The VOGTSTAR}
\label{sec:vogtstar}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/learn_map_high_snr_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/learn_map_high_snr_rect.pdf}
    \oscaption{vogtstar}{%
        Solution to the \vogtstar problem at high SNR when both the rest frame spectrum
        and the baseline are known.
        \label{fig:vogtstar_learn_map_high_snr}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.95\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \vogtstar map as a function of inclination.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}

@@

The $n^\mathrm{th}$ term of the polynomial basis
